Space and complexities of territorial systems \\\bigskip \textit{Actes des Journ{\'e}es de Rochebrune 2019}

### 2019-12-19 Docs/arxiv/v1/paper.tex
paper_trad

%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.49\linewidth]{figures/configdist_boxplot_id3642.png}
	\includegraphics[width=0.49\linewidth]{figures/configdist_boxplot_id3784.png}
	\includegraphics[width=0.49\linewidth]{figures/lambda1_alpha_colbeta.png}
	\includegraphics[width=0.49\linewidth]{figures/lambda2_alpha_colrelgrowthrate.png}
	\caption{\textbf{Estimation of local Lyapounov exponents for the reaction-diffusion model.} \textit{(Top)} Temporal profiles as descriptive statistics for $\log d(t)$ as a function of $t$, for two configurations showing a maximal fit and a maximal $\lambda_1$ value ; \textit{(Bottom left)} Value of $\lambda_1$ as a function of $\alpha$, for different values of $\beta$ (color) ; \textit{(Bottom right)} Value of $\lambda_2$ as a function of $\alpha$, for different values of $N_G / P_{max}$.}
	\label{fig:lyapounov}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/trajs_moran-dist_seed8578.png}
	\caption{\textbf{Temporal trajectories of the morphological indicators.} We show for a parameter point a sample of 50 trajectories in the morphological space (moran,distance), the color giving the level of hierarchy. In this configuration, the final variance is very large and trajectories sometimes cross others, confirming the path-dependence for morphological indicators.}
	\label{fig:morphotraj}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.49\textwidth]{figures/ex_0_tf30.png}
	\includegraphics[width=0.49\textwidth]{figures/ex_0_tf30_rsclustering321.png}\\\bigskip
	\includegraphics[width=0.49\textwidth]{figures/radius.png}
	\includegraphics[width=0.49\textwidth]{figures/profiledisteucl.png}\\
	\includegraphics[width=0.49\textwidth]{figures/distance.png}
	\includegraphics[width=0.49\textwidth]{figures/withinss.png}
	\caption{\textbf{Spatial niches of co-evolution in the RBD model.}\textit{(Top left)} Configuration generated with $N_C = 5$ centers and non-stationary parameters with closest centers, such that, in a decreasing vertical coordinate order, the weights for each center are $(w_d,w_r,w_c) = (0,1,0) ; (0,0,1) ; (1,0,1) ; (1,0,1) ; (0,0,1)$; \textit{(Top right)} Example of corresponding realization for the k-means classification, the color of cells giving the cluster; \textit{(Middle left)} Average normalized radius of clusters, for each mode and parameter configuration (color), and also for the null model of random clusters (dashed lines); \textit{(Middle right)} Average distance between lagged correlation profiles for cluster centroids; \textit{(Bottom left)} Average distance of centroids to centers; \textit{(Bottom right)} Intra-cluster variance.}
	\label{fig:rbd}
\end{figure}
%%%%%%%%%%%%%%

@@

\bibliographystyle{apalike}
\bibliography{biblio}
%\end{multicols}

>>>>

%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.49\linewidth]{configdist_boxplot_id3642.png}
	\includegraphics[width=0.49\linewidth]{configdist_boxplot_id3784.png}
	\includegraphics[width=0.49\linewidth]{lambda1_alpha_colbeta.png}
	\includegraphics[width=0.49\linewidth]{lambda2_alpha_colrelgrowthrate.png}
	\caption{\textbf{Estimation of local Lyapounov exponents for the reaction-diffusion model.} \textit{(Top)} Temporal profiles as descriptive statistics for $\log d(t)$ as a function of $t$, for two configurations showing a maximal fit and a maximal $\lambda_1$ value ; \textit{(Bottom left)} Value of $\lambda_1$ as a function of $\alpha$, for different values of $\beta$ (color) ; \textit{(Bottom right)} Value of $\lambda_2$ as a function of $\alpha$, for different values of $N_G / P_{max}$.}
	\label{fig:lyapounov}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{trajs_moran-dist_seed8578.png}
	\caption{\textbf{Temporal trajectories of the morphological indicators.} We show for a parameter point a sample of 50 trajectories in the morphological space (moran,distance), the color giving the level of hierarchy. In this configuration, the final variance is very large and trajectories sometimes cross others, confirming the path-dependence for morphological indicators.}
	\label{fig:morphotraj}
\end{figure}
%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.49\textwidth]{ex_0_tf30.png}
	\includegraphics[width=0.49\textwidth]{ex_0_tf30_rsclustering321.png}\\\bigskip
	\includegraphics[width=0.49\textwidth]{radius.png}
	\includegraphics[width=0.49\textwidth]{profiledisteucl.png}\\
	\includegraphics[width=0.49\textwidth]{distance.png}
	\includegraphics[width=0.49\textwidth]{withinss.png}
	\caption{\textbf{Spatial niches of co-evolution in the RBD model.}\textit{(Top left)} Configuration generated with $N_C = 5$ centers and non-stationary parameters with closest centers, such that, in a decreasing vertical coordinate order, the weights for each center are $(w_d,w_r,w_c) = (0,1,0) ; (0,0,1) ; (1,0,1) ; (1,0,1) ; (0,0,1)$; \textit{(Top right)} Example of corresponding realization for the k-means classification, the color of cells giving the cluster; \textit{(Middle left)} Average normalized radius of clusters, for each mode and parameter configuration (color), and also for the null model of random clusters (dashed lines); \textit{(Middle right)} Average distance between lagged correlation profiles for cluster centroids; \textit{(Bottom left)} Average distance of centroids to centers; \textit{(Bottom right)} Intra-cluster variance.}
	\label{fig:rbd}
\end{figure}
%%%%%%%%%%%%%%

@@

\begin{thebibliography}{}

\bibitem[Batty, 2018]{batty2018defining}
Batty, M. (2018).
\newblock Defining complexity in cities.
\newblock {\em Theories and Models of Urbanization, Pumain D., ed., Springer
  Series Lecture Notes in Morphogenesis}.

\bibitem[Batty and Longley, 1994]{batty1994fractal}
Batty, M. and Longley, P.~A. (1994).
\newblock {\em Fractal cities: a geometry of form and function}.
\newblock Academic Press.

\bibitem[Bedau, 2002]{bedau2002downward}
Bedau, M. (2002).
\newblock Downward causation and the autonomy of weak emergence.
\newblock {\em Principia: an international journal of epistemology},
  6(1):5--50.

\bibitem[Berry, 1964]{berry1964cities}
Berry, B.~J. (1964).
\newblock Cities as systems within systems of cities.
\newblock {\em Papers in Regional Science}, 13(1):147--163.

\bibitem[Birkin and Clarke, 2011]{birkin2011spatial}
Birkin, M. and Clarke, M. (2011).
\newblock Spatial microsimulation models: a review and a glimpse into the
  future.
\newblock In {\em Population dynamics and projection methods}, pages 193--208.
  Springer.

\bibitem[Bonnel et~al., 2014]{bonnel2014survey}
Bonnel, P., Coulombel, N., Prados, E., Sturm, P., Arnaud, E., Boittin, C.,
  Bouzouina, L., Delgado, J.~C., Capelle, T., Delons, J., et~al. (2014).
\newblock A survey on the calibration and validation of integrated land use and
  transportation models.
\newblock In {\em Symposium" Towards integrated modelling of urban systems"}.

\bibitem[Chen, 2009]{chen2009urban}
Chen, Y. (2009).
\newblock Urban gravity model based on cross-correlation function and fourier
  analyses of spatio-temporal process.
\newblock {\em Chaos, Solitons \& Fractals}, 41(2):603--614.

\bibitem[Chu, 2008]{chu2008criteria}
Chu, D. (2008).
\newblock Criteria for conceptual and operational notions of complexity.
\newblock {\em Artificial Life}, 14(3):313--323.

\bibitem[Crutchfield and Kaneko, 1987]{crutchfield1987phenomenology}
Crutchfield, J.~P. and Kaneko, K. (1987).
\newblock Phenomenology of spatio-temporal chaos.
\newblock In {\em Directions In Chaos---Volume 1}, pages 272--353. World
  Scientific.

\bibitem[Dauphin{\'e}, 1995]{dauphine1995chaos}
Dauphin{\'e}, A. (1995).
\newblock {\em Chaos, fractales et dynamiques en g{\'e}ographie}, volume~4.
\newblock GIP Reclus.

\bibitem[Day, 1981]{day1981complexity}
Day, W.~H. (1981).
\newblock The complexity of computing metric distances between partitions.
\newblock {\em Mathematical Social Sciences}, 1(3):269--287.

\bibitem[Deffuant et~al., 2015]{deffuant2015visions}
Deffuant, G., Banos, A., Chavalarias, D., Bertelle, C., Brodu, N., Jensen, P.,
  Lesne, A., M{\"u}ller, J.-P., Perrier, {\'E}., and Varenne, F. (2015).
\newblock Visions de la complexit{\'e}. le d{\'e}mon de laplace dans tous ses
  {\'e}tats.
\newblock {\em Natures Sciences Soci{\'e}t{\'e}s}, 23(1):42--53.

\bibitem[Doursat et~al., 2012]{doursat2012morphogenetic}
Doursat, R., Sayama, H., and Michel, O. (2012).
\newblock {\em Morphogenetic engineering: toward programmable complex systems}.
\newblock Springer.

\bibitem[Dupuy and Benguigui, 2015]{dupuy2015sciences}
Dupuy, G. and Benguigui, L.~G. (2015).
\newblock Sciences urbaines: interdisciplinarit{\'e}s passive, na{\"\i}ve,
  transitive, offensive.
\newblock {\em M{\'e}tropoles}, (16).

\bibitem[Favaro and Pumain, 2011]{favaro2011gibrat}
Favaro, J.-M. and Pumain, D. (2011).
\newblock Gibrat revisited: An urban growth model incorporating spatial
  interaction and innovation cycles.
\newblock {\em Geographical Analysis}, 43(3):261--286.

\bibitem[Haken and Portugali, 2016]{e18060197}
Haken, H. and Portugali, J. (2016).
\newblock Information and selforganization: A unifying approach and
  applications.
\newblock {\em Entropy}, 18(6):197.

\bibitem[Holland, 2012]{holland2012signals}
Holland, J.~H. (2012).
\newblock {\em Signals and boundaries: Building blocks for complex adaptive
  systems}.
\newblock MIT Press.

\bibitem[Krugman, 1992]{krugman1992dynamic}
Krugman, P. (1992).
\newblock A dynamic spatial model.
\newblock Working Paper. National Bureau of Economic Research.

\bibitem[Le~N{\'e}chet and Raimbault, 2015]{lenechet:halshs-01272236}
Le~N{\'e}chet, F. and Raimbault, J. (2015).
\newblock {Modeling the emergence of metropolitan transport autorithy in a
  polycentric urban region}.
\newblock In {\em {European Colloqueum on Theoretical and Quantitative
  Geography}}, Bari, Italy.

\bibitem[Manson, 2008]{manson2008does}
Manson, S.~M. (2008).
\newblock Does scale exist? an epistemological scale continuum for complex
  human--environment systems.
\newblock {\em Geoforum}, 39(2):776--788.

\bibitem[Marchionni, 2004]{marchionni2004geographical}
Marchionni, C. (2004).
\newblock Geographical economics versus economic geography: towards a
  clarification of the dispute.
\newblock {\em Environment and Planning A}, 36(10):1737--1753.

\bibitem[Mesoudi, 2017]{Mesoudi25072017}
Mesoudi, A. (2017).
\newblock Pursuing darwin's curious parallel: Prospects for a science of
  cultural evolution.
\newblock {\em Proceedings of the National Academy of Sciences},
  114(30):7853--7860.

\bibitem[Morin, 1980]{morin1980methode}
Morin, E. (1980).
\newblock {\em La M{\'e}thode, tome 2. La Vie de la Vie}.
\newblock Le Seuil.

\bibitem[Perez et~al., 2016]{perez2016agent}
Perez, P., Banos, A., and Pettit, C. (2016).
\newblock Agent-based modelling for urban planning current limitations and
  future trends.
\newblock In {\em International Workshop on Agent Based Modelling of Urban
  Systems}, pages 60--69. Springer.

\bibitem[Porumbel et~al., 2011]{porumbel2011efficient}
Porumbel, D.~C., Hao, J.~K., and Kuntz, P. (2011).
\newblock An efficient algorithm for computing the distance between close
  partitions.
\newblock {\em Discrete Applied Mathematics}, 159(1):53--59.

\bibitem[Pumain, 1997]{pumain1997pour}
Pumain, D. (1997).
\newblock Pour une th{\'e}orie {\'e}volutive des villes.
\newblock {\em Espace g{\'e}ographique}, 26(2):119--134.

\bibitem[Pumain, 2003]{pumain2003approche}
Pumain, D. (2003).
\newblock Une approche de la complexit{\'e} en g{\'e}ographie.
\newblock {\em G{\'e}ocarrefour}, 78(1):25--31.

\bibitem[Pumain, 2010]{pumain2010theorie}
Pumain, D. (2010).
\newblock Une th{\'e}orie g{\'e}ographique des villes.
\newblock {\em Bulletin de la Soci{\'e}t{\'e} g{\'e}ographie de Li{\`e}ge},
  (55):5--15.

\bibitem[Pumain, 2012]{pumain2012urban}
Pumain, D. (2012).
\newblock Urban systems dynamics, urban growth and scaling laws: The question
  of ergodicity.
\newblock In {\em Complexity Theories of Cities Have Come of Age}, pages
  91--103. Springer.

\bibitem[Pumain, 2018]{pumain2018evolutionary}
Pumain, D. (2018).
\newblock An evolutionary theory of urban systems.
\newblock In {\em International and Transnational Perspectives on Urban
  Systems}, pages 3--18. Springer.

\bibitem[Raimbault, 2017a]{raimbault2017complexity}
Raimbault, J. (2017a).
\newblock Complexity, complexities and complex knowledges.
\newblock In {\em ERC GeoDiverCity International Workshop-Theories and models
  of urbanization}.

\bibitem[Raimbault, 2017b]{raimbault2017identification}
Raimbault, J. (2017b).
\newblock Identification de causalit{\'e}s dans des donn{\'e}es
  spatio-temporelles.
\newblock In {\em Spatial Analysis and GEOmatics 2017}.

\bibitem[Raimbault, 2017c]{raimbault2017invisible}
Raimbault, J. (2017c).
\newblock Invisible bridges? scientific landscapes around similar objects
  studied from economics and geography perspectives.
\newblock In {\em 20th European Colloquium in Theoretical and Quantitative
  Geography 2017}.

\bibitem[Raimbault, 2018a]{raimbault2018calibration}
Raimbault, J. (2018a).
\newblock Calibration of a density-based model of urban morphogenesis.
\newblock {\em PloS one}, 13(9):e0203516.

\bibitem[Raimbault, 2018b]{raimbault2018caracterisation}
Raimbault, J. (2018b).
\newblock {\em Caract{\'e}risation et mod{\'e}lisation de la co-{\'e}volution
  des r{\'e}seaux de transport et des territoires}.
\newblock PhD thesis, Universit{\'e} Paris 7 Denis Diderot.

\bibitem[Raimbault, 2018c]{raimbault2018modeling}
Raimbault, J. (2018c).
\newblock Modeling the co-evolution of cities and networks.
\newblock {\em Forthcoming in Handbook of cities and networks, Rozenblat C.,
  Niel Z., eds. arXiv:1804.09430}.

\bibitem[Raimbault, 2018d]{raimbault2018relating}
Raimbault, J. (2018d).
\newblock Relating complexities for the reflexive study of complex systems.
\newblock {\em Theories and Models of Urbanization, Pumain D., ed., Springer
  Series Lecture Notes in Morphogenesis}.

\bibitem[Raimbault, 2018e]{raimbault2018urban}
Raimbault, J. (2018e).
\newblock An urban morphogenesis model capturing interactions between networks
  and territories.
\newblock {\em Mathematics of Urban Morphogenesis, D'acci L., ed., Springer
  Birkhauser Mathematics}.

\bibitem[Raimbault et~al., 2014]{raimbault2014hybrid}
Raimbault, J., Banos, A., and Doursat, R. (2014).
\newblock A hybrid network/grid model of urban morphogenesis and optimization.
\newblock In {\em 4th International Conference on Complex Systems and
  Applications (ICCSA 2014)}, pages 51--60. M. A. Aziz-Alaoui, C. Bertelle, X.
  Z. Liu, D. Olivier.

\bibitem[Reuillon et~al., 2013]{reuillon2013openmole}
Reuillon, R., Leclaire, M., and Rey-Coyrehourcq, S. (2013).
\newblock Openmole, a workflow engine specifically tailored for the distributed
  exploration of simulation models.
\newblock {\em Future Generation Computer Systems}, 29(8):1981--1990.

\bibitem[Rozenblat and Pumain, 2018]{rozenblat2018conclusion}
Rozenblat, C. and Pumain, D. (2018).
\newblock Conclusion: Toward a methodology for multi-scalar urban system
  policies.
\newblock {\em International and Transnational Perspectives on Urban Systems},
  page 385.

\bibitem[Sanders et~al., 2018]{sanders2018survival}
Sanders, L., Thomas, I., and Vacchiani-Marcuzzo, C. (2018).
\newblock On the survival of butterflies in the jungle of urban systems.
\newblock {\em Theories and Models of Urbanization, Pumain D., ed., Springer
  Series Lecture Notes in Morphogenesis}.

\bibitem[Treiber et~al., 2010]{treiber2010three}
Treiber, M., Kesting, A., and Helbing, D. (2010).
\newblock Three-phase traffic theory and two-phase models with a fundamental
  diagram in the light of empirical stylized facts.
\newblock {\em Transportation Research Part B: Methodological},
  44(8-9):983--1000.

\bibitem[Wilensky, 1999]{wilensky1999netlogo}
Wilensky, U. (1999).
\newblock Netlogo.

\bibitem[Yamu and Frankhauser, 2015]{yamu2015spatial}
Yamu, C. and Frankhauser, P. (2015).
\newblock Spatial accessibility to amenities, natural areas and urban green
  spaces: using a multiscale, multifractal simulation model for managing urban
  sprawl.
\newblock {\em Environment and Planning B: Planning and Design},
  42(6):1054--1078.

\bibitem[Zhu et~al., 2013]{zhu2013amoeba}
Zhu, L., Aono, M., Kim, S.-J., and Hara, M. (2013).
\newblock Amoeba-based computing for traveling salesman problem: Long-term
  correlations between spatially separated individual cells of physarum
  polycephalum.
\newblock {\em Biosystems}, 112(1):1--10.

\end{thebibliography}

%\end{multicols}
